DSIA: Data Systems for Interactive Analysis

### 2017-02-22 2017/paper.tex
dates

\section{Important Dates}
XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

Need to specify 3 dates:
(1) date of participation (when the workshop will be held); (2) submission deadline (for the workshop), (3) date by which we'll notice by the authors

>>>>

\section{Important Dates}

These dates are tentative, because we want to align them to the early
registration deadline of IEEE VIS 2017. This date has not been
announced yet, and we will adjust our timeline accordingly. We are
assuming the early registration deadline is 6 weeks before the
conference: roughly August 15th.

\begin{itemize}
  \item Date of participation: Sunday, Monday, or Tuesday (Oct 1st,
    2nd, or 3rd)
  \item Submission Deadline: July 15th.
  \item Notification Deadline: August 1st.
\end{itemize}
